---
title: "Add Code Eligibility Coding Exercise - Calint NOrhdime-Maestas"
format: html
editor: visual
---

## Instructions

Run the following code chunks and complete all necessary prompts with your own code. Once finished, follow the submission instructions on the Github Repository's README.

## Setup

```{r load-packages}
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(dplyr)
library(paletteer) # Added this for colors
```

## Data Exploration

Run the following code cell to explore the data a bit.

```{r data-exploration}


# Create palmer penguins dataframe
penguins_df <- penguins
# Examine the structure of the dataset
str(penguins_df)
glimpse(penguins_df)

# Generate summary statistics
summary(penguins_df)

```

## Data Cleaning

Complete the following data cleaning steps in the `penguins_df` dataframe:

1.  Remove observations with missing values
2.  Create a new column in `penguins_df`called `length_mass` that measures the length to mass ratio of each penguin.

```{r data-cleaning}

# Remove missing values
penguins_df <- penguins_df %>% 
  drop_na() %>% 


# Create length_mass column that measures length to mass ratio for each penguin
  # note: did not specify whether bill length or flipper length, I'll go with the flipper length because flippers are cute
  mutate(length_mass = flipper_length_mm / body_mass_g)

```

## Data Visualization

Use `ggplot` to make a visualization of your choice with the penguin data. Be sure you include the following in your visualization:

-   An updated title

-   Updated axis labels

-   A color palette/ colors of your choosing (not default ggplot colors)

-   Comments!

```{r data-viz}
penguins_df %>% 
  ggplot(aes(x = flipper_length_mm, y = body_mass_g, color = species)) + # specify data for axes
  geom_point() + # scatterplot
  labs( # add labels
    x = "Flipper length", # x axis
    y = "Body Mass (g)", # y axis
    title = "Penguin flipper length and body mass, across species", # title for top of plot
    caption = "Color palette credit: TayloR Swift, album midnights, by asteves" # caption at bottom with credit for color palette
  ) + 
  theme_minimal() + # update theme to my fave, low key gridded background, makes the data pop
  scale_color_manual(values = paletteer_d("tayloRswift::midnights")) # color by species using Taylor swifts midnigths palette
```

That's it! Head back to the README on the Github repo for submission instructions.
